Summary Tables

### 2020-03-19 summary_tables_outcomes.Rmd
Add unit and comment out DT

## Who Hit Whom matrix

@@

### DT - Who hit whom matrix for all case cities {#whw_all}
Baseline

```{r dt}

#for (cs in names(all_whw)){
td <- NULL

cs <- 'Baseline'

fname <- paste("whw_", var, ".csv")

td <- st[[var]]

DT::datatable(td, 
              extensions = 'Buttons',
              escape = FALSE,
              rownames = FALSE,
              options = list(dom = 'Bfrtip',
                             buttons = 
                               list('colvis', list(
                                 extend = 'collection',
                                 buttons = list(list(extend='csv',
                                                     filename = fname),
                                                list(extend='excel',
                                                     filename = fname)),
                                 text = 'Download'
                               )),
                             scrollX = TRUE,
                             pageLength = nrow(td),
                             order=list(list(2,'desc')),
                             columnDefs = list(list(visible=FALSE, targets=c(1:(ncol(td) - 1))))))

# }

@@

>>>>

## Who Hit Whom matrix (normalized to annual figures)

@@

<!-- ### DT - Who hit whom matrix for all case cities {#whw_all} -->
<!-- Baseline -->

<!-- ```{r dt} -->

<!-- #for (cs in names(all_whw)){ -->
<!-- td <- NULL -->

<!-- cs <- 'Baseline' -->

<!-- var <- scen_lt %>% filter(scen_name == cs) %>% dplyr::select(val) %>% as.character() -->

<!-- fname <- paste("whw_", var, ".csv") -->

<!-- td <- st[[var]] -->

<!-- DT::datatable(td,  -->
<!--               extensions = 'Buttons', -->
<!--               escape = FALSE, -->
<!--               rownames = FALSE, -->
<!--               options = list(dom = 'Bfrtip', -->
<!--                              buttons =  -->
<!--                                list('colvis', list( -->
<!--                                  extend = 'collection', -->
<!--                                  buttons = list(list(extend='csv', -->
<!--                                                      filename = fname), -->
<!--                                                 list(extend='excel', -->
<!--                                                      filename = fname)), -->
<!--                                  text = 'Download' -->
<!--                                )), -->
<!--                              scrollX = TRUE, -->
<!--                              pageLength = nrow(td), -->
<!--                              order=list(list(2,'desc')), -->
<!--                              columnDefs = list(list(visible=FALSE, targets=c(1:(ncol(td) - 1)))))) -->

<!-- # } -->

@@

<!-- YLLs total (for the city based on real population size) by age group by scenario -->
